Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-10-04 manuscript.Rmd
Code update with full OSF integration, added extra figure.

# check which packages are installed, install the missing ones, and activate
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'osfr','FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

Figure \@ref(fig:EEGdata) shows the results for EEG. Figure \@ref(fig:EEGdata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:EEGdata)b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \@ref(fig:EEGdata)c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \@ref(fig:EEGdata)f-h show the CRFs at the second harmonic. 
What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig. \@ref(fig:EEGdata)c) and second (fig. \@ref(fig:EEGdata)f) harmonics are showing very high summation of binocular signals compared to the pupillometry. The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses. This is especially clear at the highest contrasts. This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry. For the cross-frequency condition at 2 Hz and 4 Hz (fig. \@ref(fig:EEGdata)d and \@ref(fig:EEGdata)g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig. \@ref(fig:EEGdata)e) and 3.2 Hz (fig. \@ref(fig:EEGdata)h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a  linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex. 
```{r include=FALSE, results='hide'}

@@

tempmasksP <- array(0,dim=c(length(d),6,5))
tempmeansP <- tempmasksP
tempmasksE <- array(0,dim=c(length(d),64,6,5))
tempmeansE <- tempmasksE
tempmeansE2 <- tempmeansE
tempmasksE2 <- tempmasksE
tempspectraP <- array(0,dim=c(length(d),300))
tempspectraE <- array(0,dim=c(length(d),300))
tempwavesP <- array(0,dim=c(length(d),1680))
tempwavesE <- array(0,dim=c(length(d),14000))

@@

  tempmasksP[s,,] <- cleanmasksP
  tempmeansP[s,,] <- cleanmeansP
  tempspectraP[s,] <- meanspectraP
  tempspectraE[s,] <- meanspectraE
  tempwavesP[s,] <- meanwavesP
  tempwavesE[s,] <- meanwavesE
  tempmeansE[s,,,] <- cleanmeansE
  tempmasksE[s,,,] <- cleanmasksE
  tempmeansE2[s,,,] <- cleanmeansE2
  tempmasksE2[s,,,] <- cleanmasksE2

@@

tempspectraP <- tempspectraP[-c(2,4,13,20,26),]

@@

    temp <- tempmeansP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansP[cond,level] <- mbs$meanamp
    cleanmeansPCI[1,cond,level] <- mbs$lowerCI
    cleanmeansPCI[2,cond,level] <- mbs$upperCI
    }

    temp <- tempmasksP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
          mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksP[cond,level] <- mbs$meanamp
    cleanmasksPCI[1,cond,level] <- mbs$lowerCI
    cleanmasksPCI[2,cond,level] <- mbs$upperCI
}

      temp <- apply(tempmeansE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansEav[cond,level] <- mbs$meanamp
    cleanmeansEavCI[1,cond,level] <- mbs$lowerCI
    cleanmeansEavCI[2,cond,level] <- mbs$upperCI
      }

temp <- apply(tempmasksE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksEav[cond,level] <- mbs$meanamp
    cleanmasksEavCI[1,cond,level] <- mbs$lowerCI
    cleanmasksEavCI[2,cond,level] <- mbs$upperCI
        }

temp <- apply(tempmeansE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE2av[cond,level] <- mbs$meanamp
    cleanmeansE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmeansE2avCI[2,cond,level] <- mbs$upperCI
        }

      temp <- apply(tempmasksE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE2av[cond,level] <- mbs$meanamp
    cleanmasksE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmasksE2avCI[2,cond,level] <- mbs$upperCI
        }

@@

      temp <- tempmeansE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE[ch,cond,level] <- mbs$meanamp
    cleanmeansECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansECI[2,ch,cond,level] <- mbs$upperCI
}

      temp <- tempmasksE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE[ch,cond,level] <- mbs$meanamp
    cleanmasksECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksECI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- tempmeansE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE2[ch,cond,level] <- mbs$meanamp
    cleanmeansE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansE2CI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- tempmasksE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE2[ch,cond,level] <- mbs$meanamp
    cleanmasksE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksE2CI[2,ch,cond,level] <- mbs$upperCI
        }

@@

        temp <- tempspectraP[,f]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
meanspectraP[f] <- mbs$meanamp
meanspectraPCI[1,f] <- mbs$lowerCI
meanspectraPCI[2,f] <- mbs$upperCI
      }

        temp <- tempspectraE[,f]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
meanspectraE[f] <- mbs$meanamp
meanspectraECI[1,f] <- mbs$lowerCI
meanspectraECI[2,f] <- mbs$upperCI
      }
}

meanwavesP <- NULL
meanwavesE <- NULL
meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))
meanwavesECI <- array(0,dim=c(2,dim(tempwavesE)[2]))
nsubjs <- dim(tempwavesP)[1]
for (t in 1:dim(tempwavesP)[2]){
  temp <- tempwavesP[,t]
  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
  meanwavesP[t] <- mean(temp[i])
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
  meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
}

for (t in 1:dim(tempwavesE)[2]){
    temp <- tempwavesE[,t]
  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
  meanwavesE[t] <- mean(temp[i])
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
  meanwavesECI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
}

save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes'))

@@

## Experiment 2
The results from the second experiment are shown in \@ref(fig:TFdata). Figure \@ref(fig:TFdata)a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz). We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics. However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded. This is also reflected in figure \@ref(fig:TFdata)b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz. The rest of figure \@ref(fig:TFdata)b is showing the response at each stimulation frequency. We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz. In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig. \@ref(fig:TFdata)c), suggesting that binocular facilitation is happening at higher frequencies. However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \@ref(fig:TFdata)c). The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
```{r include=FALSE, results='hide'}

@@

When the match was presented monocularly (only one eye was presented with a flickering stimulus), we observe that, for the match to appear to flicker similarly to the standard, the contrast in that eye was set to be around double the contrast of the standard. When the flicker was presented only to the left eye, for the 48 \% contrast, the contrast of the match was around 90 \%, and, for the 24 \% contrast, the contrast of the match was around 57 \%. When the flicker was presented only to the right eye, for the 48 \% contrast, the contrast in the right eye was around 96 \%, and, for the 24 \% contrast, the contrast was around 50 \%. When looking at the intermediate condition, we can see that the points, for both contrast conditions, seem to fall along the main diagonal representing the linear summation prediction, with the results for the 24 \% condition showing a very strong summation that seem to exceed this prediction. Overall, these results seem to suggest that the way we perceive temporal luminance modulations follows near linear combination rules, which is in line with the processes observed in the visual cortex in experiment 1 (fig. \@ref(fig:EEGdata)).
```{r include=FALSE, results='hide'}

@@

tempmasksP <- array(0,dim=c(length(d),6,5))
tempmeansP <- tempmasksP
tempmasksE <- array(0,dim=c(length(d),64,6,5))
tempmeansE <- tempmasksE
tempmeansE2 <- tempmeansE
tempmasksE2 <- tempmasksE

>>>>

# check which packages are installed, install the missing ones, and activate
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','osfr') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

Figure \@ref(fig:EEGdata) shows the results for EEG. Figure \@ref(fig:EEGdata)a is showing the group average waveform for binocular presentation. Figure \@ref(fig:EEGdata)b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics. Figures \@ref(fig:EEGdata)c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \@ref(fig:EEGdata)f-h show the CRFs at the second harmonic. 
What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig. \@ref(fig:EEGdata)c) and second (fig. \@ref(fig:EEGdata)f) harmonics are showing very high summation of binocular signals compared to the pupillometry. The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses. This is especially clear at the highest contrasts. This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry. For the cross-frequency condition at 2 Hz and 4 Hz (fig. \@ref(fig:EEGdata)d and \@ref(fig:EEGdata)g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals. This pattern is also observable in the cross-frequency condition at 1.6 (fig. \@ref(fig:EEGdata)e) and 3.2 Hz (fig. \@ref(fig:EEGdata)h). This pattern of results seems to suggest that processing of temporal luminance modulations happens in a  linear way in the visual cortex. Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.

@@

allmasksP <- array(0,dim=c(length(d),6,5))
allmeansP <- allmasksP
allmasksE <- array(0,dim=c(length(d),64,6,5))
allmeansE <- allmasksE
allmeansE2 <- allmeansE
allmasksE2 <- allmasksE
allspectraP <- array(0,dim=c(length(d),300))
allspectraE <- array(0,dim=c(length(d),300))
allwavesP <- array(0,dim=c(length(d),1680))
allwavesE <- array(0,dim=c(length(d),14000))

@@

  allmasksP[s,,] <- cleanmasksP
  allmeansP[s,,] <- cleanmeansP
  allspectraP[s,] <- meanspectraP
  allspectraE[s,] <- meanspectraE
  allwavesP[s,] <- meanwavesP
  allwavesE[s,] <- meanwavesE
  allmeansE[s,,,] <- cleanmeansE
  allmasksE[s,,,] <- cleanmasksE
  allmeansE2[s,,,] <- cleanmeansE2
  allmasksE2[s,,,] <- cleanmasksE2

@@

allspectraP <- allspectraP[-c(2,4,13,20,26),]

@@

    temp <- allmeansP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansP[cond,level] <- mbs$meanamp
    cleanmeansPCI[1,cond,level] <- mbs$lowerCI
    cleanmeansPCI[2,cond,level] <- mbs$upperCI
    }

    temp <- allmasksP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
          mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksP[cond,level] <- mbs$meanamp
    cleanmasksPCI[1,cond,level] <- mbs$lowerCI
    cleanmasksPCI[2,cond,level] <- mbs$upperCI
}

      temp <- apply(allmeansE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansEav[cond,level] <- mbs$meanamp
    cleanmeansEavCI[1,cond,level] <- mbs$lowerCI
    cleanmeansEavCI[2,cond,level] <- mbs$upperCI
      }

temp <- apply(allmasksE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksEav[cond,level] <- mbs$meanamp
    cleanmasksEavCI[1,cond,level] <- mbs$lowerCI
    cleanmasksEavCI[2,cond,level] <- mbs$upperCI
        }

temp <- apply(allmeansE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE2av[cond,level] <- mbs$meanamp
    cleanmeansE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmeansE2avCI[2,cond,level] <- mbs$upperCI
        }

      temp <- apply(allmasksE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE2av[cond,level] <- mbs$meanamp
    cleanmasksE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmasksE2avCI[2,cond,level] <- mbs$upperCI
        }

@@

      temp <- allmeansE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE[ch,cond,level] <- mbs$meanamp
    cleanmeansECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansECI[2,ch,cond,level] <- mbs$upperCI
}

      temp <- allmasksE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE[ch,cond,level] <- mbs$meanamp
    cleanmasksECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksECI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- allmeansE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE2[ch,cond,level] <- mbs$meanamp
    cleanmeansE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansE2CI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- allmasksE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE2[ch,cond,level] <- mbs$meanamp
    cleanmasksE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksE2CI[2,ch,cond,level] <- mbs$upperCI
        }

@@

        temp <- allspectraP[,f]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
meanspectraP[f] <- mbs$meanamp
meanspectraPCI[1,f] <- mbs$lowerCI
meanspectraPCI[2,f] <- mbs$upperCI
      }

        temp <- allspectraE[,f]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
meanspectraE[f] <- mbs$meanamp
meanspectraECI[1,f] <- mbs$lowerCI
meanspectraECI[2,f] <- mbs$upperCI
      }
}

meanwavesP <- NULL
meanwavesE <- NULL
meanwavesPCI <- array(0,dim=c(2,dim(allwavesP)[2]))
meanwavesECI <- array(0,dim=c(2,dim(allwavesE)[2]))
nsubjs <- dim(allwavesP)[1]
for (t in 1:dim(allwavesP)[2]){
  temp <- allwavesP[,t]
  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
  meanwavesP[t] <- mean(temp[i])
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
  meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
}

for (t in 1:dim(allwavesE)[2]){
    temp <- allwavesE[,t]
  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
  meanwavesE[t] <- mean(temp[i])
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
  meanwavesECI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
}

save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes','allmeansP','allmeansE','allmeansE2'))

@@

# generate plot showing the bin:mon ratio for three data sets

contrastsdB <- 20*log10(c(6,12,24,48,96))
electrodeindices <- match(targetelectrodes,electrodes)-2

allPratios <- 20*log10(abs(allmeansP[,2,])/abs(allmeansP[,1,]))
allEratios <- 20*log10(abs(apply(allmeansE[,electrodeindices,2,],c(1,3),mean))/abs(apply(allmeansE[,electrodeindices,1,],c(1,3),mean)))
allE2ratios <- 20*log10(abs(apply(allmeansE2[,electrodeindices,2,],c(1,3),mean))/abs(apply(allmeansE2[,electrodeindices,1,],c(1,3),mean)))

PratiosCI <- matrix(0,nrow=2,ncol=5)
EratiosCI <- matrix(0,nrow=2,ncol=5)
E2ratiosCI <- matrix(0,nrow=2,ncol=5)
for (level in 1:5){
    bspop <- NULL
    for (n in 1:nbootstraps){
      bspop[n] <- mean(sample(allPratios[,level],nrow(allPratios),replace=TRUE))
    }
    PratiosCI[,level] <- quantile(bspop,c((1-0.68)/2,1-((1-0.68)/2)))
     bspop <- NULL
    for (n in 1:nbootstraps){
      bspop[n] <- mean(sample(allEratios[,level],nrow(allEratios),replace=TRUE))
    }
    EratiosCI[,level] <- quantile(bspop,c((1-0.68)/2,1-((1-0.68)/2)))
    bspop <- NULL
    for (n in 1:nbootstraps){
      bspop[n] <- mean(sample(allE2ratios[,level],nrow(allE2ratios),replace=TRUE))
    }
    E2ratiosCI[,level] <- quantile(bspop,c((1-0.68)/2,1-((1-0.68)/2)))
}

plotlims <- c(15,40,-3,12)  
ticklocsx <- contrastsdB
ticklabelsx <-c(6,12,24,48,96) 
ticklocsy <- seq(-3,12,3)    # locations of tick marks on y axis
ticklabelsy <- c(expression(1/sqrt(2)),'1',expression(sqrt(2)),'2',expression(2*sqrt(2)),'4')

pdf("Figures/BSratios.pdf", onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

arrows(contrastsdB,colMeans(allPratios),contrastsdB,PratiosCI[1,],lwd=3,col=colpal[3],length=0.05,angle=90)
arrows(contrastsdB,colMeans(allPratios),contrastsdB,PratiosCI[2,],lwd=3,col=colpal[3],length=0.05,angle=90)
arrows(contrastsdB,colMeans(allEratios),contrastsdB,EratiosCI[1,],lwd=3,col=colpal[4],length=0.05,angle=90)
arrows(contrastsdB,colMeans(allEratios),contrastsdB,EratiosCI[2,],lwd=3,col=colpal[4],length=0.05,angle=90)
arrows(contrastsdB,colMeans(allE2ratios),contrastsdB,E2ratiosCI[1,],lwd=3,col=colpal[5],length=0.05,angle=90)
arrows(contrastsdB,colMeans(allE2ratios),contrastsdB,E2ratiosCI[2,],lwd=3,col=colpal[5],length=0.05,angle=90)

lines(contrastsdB,colMeans(allPratios), col=colpal[3], lwd=3, cex=0.5)
lines(contrastsdB,colMeans(allEratios), col=colpal[4], lwd=3, cex=0.5)
lines(contrastsdB,colMeans(allE2ratios), col=colpal[5], lwd=3, cex=0.5)

points(contrastsdB,colMeans(allPratios), pch = 21, col='black', bg=colpal[3], cex=1.6, lwd=3) 
points(contrastsdB,colMeans(allEratios), pch = 22, col='black', bg=colpal[4], cex=1.6, lwd=3)
points(contrastsdB,colMeans(allE2ratios), pch = 23, col='black', bg=colpal[5], cex=1.6, lwd=3)

legend(15,12,c('Pupillometry','EEG 1F', 'EEG 2F'), pch=21:23, pt.bg=colpal[3:5],box.lwd=2,pt.cex=1.6,pt.lwd=3)

```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types.", fig.align="center", echo=FALSE}

knitr::include_graphics(paste0(figdir,'BSratios.pdf'))

## Experiment 2
The results from the second experiment are shown in \@ref(fig:TFdata). Figure \@ref(fig:TFdata)a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz). We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics. However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded. This is also reflected in figure \@ref(fig:TFdata)b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz. The rest of figure \@ref(fig:TFdata)b is showing the response at each stimulation frequency. We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz. In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig. \@ref(fig:TFdata)c), suggesting that binocular facilitation is happening at higher frequencies. However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \@ref(fig:TFdata)c). The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.

@@

When the match was presented monocularly (only one eye was presented with a flickering stimulus), we observe that, for the match to appear to flicker similarly to the standard, the contrast in that eye was set to be around double the contrast of the standard. When the flicker was presented only to the left eye, for the 48 \% contrast, the contrast of the match was around 90 \%, and, for the 24 \% contrast, the contrast of the match was around 57 \%. When the flicker was presented only to the right eye, for the 48 \% contrast, the contrast in the right eye was around 96 \%, and, for the 24 \% contrast, the contrast was around 50 \%. When looking at the intermediate condition, we can see that the points, for both contrast conditions, seem to fall along the main diagonal representing the linear summation prediction, with the results for the 24 \% condition showing a very strong summation that seem to exceed this prediction. Overall, these results seem to suggest that the way we perceive temporal luminance modulations follows near linear combination rules, which is in line with the processes observed in the visual cortex in experiment 1 (fig. \@ref(fig:EEGdata)).

@@

allmasksP <- array(0,dim=c(length(d),6,5))
allmeansP <- allmasksP
allmasksE <- array(0,dim=c(length(d),64,6,5))
allmeansE <- allmasksE
allmeansE2 <- allmeansE
allmasksE2 <- allmasksE
